Study of the numerical solution of X-Modes equations around the hybrid resonnance

### 2015-01-20 report/intro.tex
adding macros.sty

 As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
 \begin{align}
-\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
\mu_0 \partial_t \Hbf + \curl\, \E = 0
\end{align}
coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions
\be
m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
\ee
Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current, 
$\ubf_e$ is the velocity of electrons and $B_0$ is the background magnetic field.  
We denote by $e<0$ the value of the charge of electrons and by $\m_e$ the electron mass.
Assuming that $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, we obtain the following system of equations 
\begin{align}
\label{eq:main_model}
\begin{split}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\nonumber\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y\nonumber
\end{split}
\end{align}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
In this work we look at a simplification of this model obtained after 
the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model (\ref{eq:main_model}) can be rewritten as follows
\begin{align}
\label{eq:main_model_theta}
\begin{split}
\epsilon_0\partial_t E_{x}-\theta H=-eN_e u_x,\nonumber\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
\mu_0\partial_t H+\partial_x E_y-\theta E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.
\end{split}
\end{align}
The energy of this system can be expressed as \cite{}
\begin{align*}

>>>>

 As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
 \begin{align}
-\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
\mu_0 \partial_t \Hbf + \curl\, \E = 0
\end{align}
coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions
\be
m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
\ee
Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current, 
$\ubf_e$ is the velocity of electrons and $B_0$ is the background magnetic field.  
We denote by $e<0$ the value of the charge of electrons and by $m_e$ the electron mass.
Assuming that $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, we obtain the following system of equations 
\begin{align}
\label{eq:main_model}
\begin{split}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{split}
\end{align}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
In this work we look at a simplification of this model obtained after 
the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model (\ref{eq:main_model}) can be rewritten as follows
\begin{align}
\label{eq:main_model_theta}
\begin{split}
\epsilon_0\partial_t E_{x}-\theta H=-eN_e u_x,\nonumber\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
\mu_0\partial_t H+\partial_x E_y-\theta E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.
\end{split}
\end{align}
The energy of this system can be expressed as \cite{}
\begin{align*}
